### 2021-04-05 papers/SYRCoSE/future.tex

Finally, we plan to mechanize in Coq classical results 
that connect various classes of event structures  
by isomorphishm of configurations~\cite{Nielsen-al:1981, Boudol-Castellani:1991}. 
It will allow to easily establish the connection between operational and denotational 
semantics of concurrent languages.

>>>>

Finally, we plan to mechanize in Coq classical results 
that connect various classes of event structures%  
~\cite{Nielsen-al:1981, Boudol-Castellani:1991}. 
It would allow us to easily establish the connection between operational and denotational 
semantics of concurrent languages.
